Reproducibility of SNP calling in multiple sequencing runs from single tumors

### 2014-06-06 PAPER/rough_draft.tex
added a bibliography to this paper

All sequence data came from The Cancer Genome Atlas (TCGA) Gliobastoma multiforme (GBM) data set. We downloaded raw reads in (XXX format) using (CGHub?) on (date) for 68 patients. For each patient, data consisted of one set of rads taken from blood DNA, and two sets of reads taken from tumor DNA. In 55 cases, the two sets of reads from tumor DNA were one set of reads from whole genome sequencing (WGS) and one set of reads from whole genome sequencing with amplification (WGA). In 13 cases, the two sets of reads from tumor DNA were one set of reads pre-readiation treatment and one set post-radiation treatment. We developed a pipeline to align all reads to HG19. This pipeline used (bowtie?) for alignment and (bedtools? whatever -- quality control...) We used SomaticSniper to align each tumor sequence with it's corresponding blood sequence. We then filtered the SomaticSniper data using 8 custom filters. These removed (i) , (ii) , (iii) , (iv) , (v) , (vi) , (vii) , and (viii) . All custom code is available in a github repository, located at (webaddress). In addition to sequence data, filter 6 uses dbSNP, version 137, to find common SNPs among the putative mutaitons called by SomaticSniper.

@@

We used custom python scripts, available in the above github repository, to perform simple calculations and data operations. We used R to do statistics and generate figures, and this code is also availabel in the git repository.

@@

>>>>

All sequence data came from The Cancer Genome Atlas (TCGA) Research Network's Gliobastoma multiforme (GBM) data set \cite{TCGA-GBM}. We downloaded raw reads in .bam files from 68 patients using CGHub \cite{CGHub}. For each patient, data consisted of one set of reads taken from blood DNA, and two sets of reads taken from tumor DNA. In 55 cases, the two sets of reads from tumor DNA were one set of reads from whole genome sequencing (WGS) and one set of reads from whole genome sequencing with amplification (WGA). In 13 cases, the two sets of reads from tumor DNA were one set of reads pre-readiation treatment and one set post-radiation treatment. We developed a pipeline to align all reads to HG19. This pipeline used picard, BWA for alignment, SamTools, GATK, and custom python code. We used SomaticSniper \cite{SomaticSniper} to align each tumor sequence with it's corresponding blood sequence, then filtered the SomaticSniper data using 8 custom filters. These removed (i) , (ii) , (iii) , (iv) , (v) , (vi) , (vii) , and (viii) . All custom code is available in a github repository, located at (webaddress). In addition to sequence data, filter 6 uses dbSNP, version 137, to find common SNPs among the putative mutaitons called by SomaticSniper.

@@

We used custom python scripts, available in the above github repository, to perform simple calculations and data operations. We used R \cite{Rsoftware} to do statistics and generate figures, and this code is also available in the git repository.

@@

\bibliography{TCGA_bib}
\bibliographystyle{plain}
